\documentclass[line, mm]{sampleCV}
\usepackage{hyperref}
\usepackage{geometry}
\geometry{
	a4paper,
	total={170mm,257mm},
	left=10mm,
	top=10mm,
	bottom=50mm,
}
\begin{document}

\name{\Large Shahryar Soltanpour}
\begin{resume}

	% Contact Information
    \section{\mysidestyle Contact\\Information}
    
   e-mail: shahryar.soltanpour@gmail.com\\
    mobile: +1 403-827-9737
    
    \section{\mysidestyle Personal Information}
   
    Birthday: May $8^{th}$, 1997

	% Research Interests
	\section{\mysidestyle About}
	I'm a skilled software engineer with nearly 4 years of working experience in Iranian top IT companies, and currently studying MSc of computer science (software engineering specialization) at UofC. \\
	I'm interested in everything related to software engineering and big data technologies. Also, engaged with leadership skills and love to work as a team. 
    
\section{\mysidestyle Education}
	\begin{list2}
	\setlength\itemsep{0.5em}
	\item \textbf{University of Calgary}\vspace{2mm}\\\vspace{1mm}
	\textsl{MSc in Computer Science (Software Engineering)} \hfill \textbf{ Jan. 2021 -- Present}\\ Under the supervision of Professor Robert Walker%
	
	
    \item \textbf{University of Tehran}, Tehran, Iran \vspace{2mm}\\\vspace{1mm}
    \textsl{Bachelor of Science in Software Engineering} \hfill \textbf{ Sep. 2015 -- Jun. 2020}\vspace{-3mm}\\\vspace{-1mm}%
    \begin{list2}
        \item GPA: 17.43/20
       	\item last year GPA: 18.59/20
       	
       	\iffalse
			item Selected courses (out of 20): 
			\begin{list2}
			\item Internet Engineering: 20			
			\item Network Security: 20
			\item Introduction to Cryptocurrency: 20
			\item Software Engineering: 19.2
			\item Software Testing: 19.1
			\item Advanced Software Design: 18.33
			\item Design and Analysis of Algorithms: 19.1    
			\item Formal Methods in Software Engineering: 18.6
			\item Compiler Design and Implementation: 18.5
			\item Theory of Formal Languages and Automata: 19.25
			\end{list2}
	\fi
    \end{list2}


\item \textbf{Allame Helli 1 School} \vspace{2mm}\\\vspace{1mm}
\textsl{Diploma in Mathematics and Physics Discipline} \hfill \textbf{ 2008 -- 2015}%
 \begin{list2}
	\item GPA: 19.91/20 \
	\end{list2}
\end{list2}
	
\section{\mysidestyle Professional Experience}

\begin{list2}

\item \textbf{Software Engineer at \textit{Divar}}(Aug. 2019 - Dec. 2020) (1 Year, 4 Months): \\
\hangindent=1em
\hangafter=1
Divar is the leading application for online classified ads, and one of the most prominent Iranian companies in Information Technology, having more than 40 million users. In Divar, we were developing using Go and Python languages and Django as the framework. Our deployment was being done using Kubernetes. \\ My main responsibilities during my career are listed below:
\begin{itemize}
	\item Designing system for new features, by writing 'design docs' and implementing them.
	\item Development of designed features, create merge requests, and deploy them on production servers.
	\item Maintaining services. As the owner of some services, I had to make sure that my services are operating properly 24/7. 
	\item Reviewing codes. As the system owner, I was responsible to evaluate merge requests on my owned services then merge and deploy them.
	\item Designing system for new features, by writing 'design docs' and implementing them.
	\item Member of the interview committee. Attending interviews with new people who wanted to enter the company, and helping the company hire the best software engineers.
\end{itemize}



\item \textbf{Software Enginner at \textit{Pegah Co. (known as Tapsell)}}] (Sep. 2017 - Aug. 2019) (2 Years):
\hangindent=1em
\hangafter=1

Tapsell is the leading company in the online advertising industry in Iran.
\begin{list2}
\item \textbf{ \textit{Mediaad}(Jun. 2018 - Aug. 2019):}\\
During my experience in Mediaad, I implemented a video player platform, helping website owners to upload and stream their video files, see statistics for each video and also earn money by showing advertisements. I also implemented the dashboard of this platform using Angular 6.\\
I also implemented some features in Mediaad platform, such as retargeting feature. 
I worked with Spring Boot and Kotlin and I got to work with big data processing tools such as Kafka streams, Elastic Search, Cassandra DB and I got familiar with Apache Spark.
\hangindent=1em
\hangafter=1
\item \textbf{\textit{Backtory}(Jan. 2018 - Jun. 2018):}\\	
Backtory is a CDN, storage and streaming service provider startup. 
During my experience in Backtory, I worked with Spring Boot framework using Kotlin as the programming language and I became skilled in them. 
I also learned and worked with HAProxy and Nginx as web servers and load balancers.

\end{list2}

%\begin{flushleft}
\hangindent=1em
\hangafter=1
\item \textbf{Software Engineering Intern at \textit{Rahnema College}} (July 2017-Aug. 2017) (2 Months) : \\
 In this cycle of Rahnema College our team launched Unagi, a location based social network application.In this project, I focused on iOS and Android application development using React-Native and React-Redux	 and I also focused on server-side development using Node.JS Express framework.This project gave me a chance to get to know and apply the Scrum methodology and Git VCS.
%\end{flushleft}



\end{list2}

\section{\mysidestyle Research\\Experience} 

\begin{list2}
	
	\item \textbf{َUndergraduate Research}(Jul. 2019 - Oct. 2019): \\
	\textbf{Real-time verification and evaluation of algorithms efficiency in distributed actor based systems}\\
	Using java language to compile and run Rebeca codes with different policies and measure some metrics to find the best algorithm.\\
	\href{http://rebeca-lang.org/}{\textit{Rebeca}} (Reactive Objects Language) is an actor-based language with a formal foundation, designed in an effort to bridge the gap between formal verification approaches and real applications. It can be considered as a reference model for concurrent computation, based on an operational interpretation of the actor model. It is also a platform for developing object-based concurrent systems in practice.\\
	Under supervision of \textbf{Dr. Fatemeh Ghassemi}.
	\\
	\item \textbf{Blockchain, CryptoCurrency and Digital Currencies}	\\
	I've passed \textit{Introduction to Cryptocurrency} course as my master's degree course and I got the mark 20/20. \\ 
	During this course, I studied several essays about Bitcoin, Ethereum and blockchain and did some computer assignments to use make Bitcoin transactions in P2PKH and P2SH modes and broadcast them to the blockchain.
	I also did some computer assignments to make a simple application using Solidity,  web3.js and Truffle framework in order to deeply understand smart contracts.\\
	Under supervision of \textbf{Dr. Behnam Bahrak}.
\end{list2}



\section{\mysidestyle Honors and\\Awards} 
\begin{list2}
\item Ranked $241^{st}$ (regional rank), and $368^{th}$ (national rank) in the National Universities Entrance Examination among more than 318,000 contestants, 2015
\item Ranked $3^{rd}$ among Undergraduate Students in Software Engineering College and winner of FoE (Faculty of Engineering) prize, University of Tehran (2015-2017)
\end{list2}


\section{\mysidestyle Open Source Projects}
\begin{list2}

\item \textbf {Implement a web-based freelancing application for Internet Engineering course. Using Java for back-end and React for front-end development.(Source Code: \href{https://github.com/sh-soltanpour/neyanboon}{\textit{Backend}} and 
	\href{https://github.com/sh-soltanpour/daf}{\textit{Frontend}})
} 

%\item \textbf {Implement a bitcoin client to make bitcoin transactions in both P2PKH and P2SH modes using Python and Bitcoin library. (Source Code: \href{https://github.com/sh-soltanpour/splitwise}{\textit{Splitwise}})}

 
\item \textbf {Implement Splitwise application using smart contracts using technologies such as Truffle, Solidity language and web3.js (Source Code: \href{https://github.com/sh-soltanpour/splitwise}{\textit{Splitwise}}
		)
}
\item \textbf {Implement a compiler for an actor based language named Atalk in compiler design course. (Source Code: \href{https://github.com/sh-soltanpour/Atalk-Compiler}{\textit{Atalk}}
	)
}

\item \textbf {Implement a location based social netowrk named Unagi during Rahnema College internship. Backend was coded using NodeJs Express and Android and iOS applications were coded using React Native. (Source Code: \href{https://github.com/sh-soltanpour/UnagiServer}{\textit{Backend}} and 
	\href{https://github.com/sh-soltanpour/UnagiApp}{\textit{Frontend}}
	)
}  

%\item \textbf{Backend development of judge website in ACM Data Analysis Contest (held by Tapsi) using Laravel framework.}
%\item \textbf{Programming a Telegram bot for etuts.ir website (@etutsbot) using PHP}(March 2017)
%\item \textbf{Programming a server-client based library application using C++}(June 2016)
%\item \textbf{Programming a sample of BoxBoy game using SDL library C++}(March2016)

\end{list2}

	% TAship
\section{\mysidestyle Teaching Assistantship}
\textbf{Internet Engineering} \hfill \textbf{Spring 2020}\\
{\it Instructor:  Dr. Ehsan Khamespanah}
\\
\textbf{Chief TA} of the course. Responsible for managing all course projects to be designed, delivered and graded.


\textbf{Systems Analysis and Design} \hfill \textbf{Spring 2019}\\
{\it Instructor:  Dr. Fatemeh Ghassemi}
\\
\textbf{Chief TA} of the course. Responsible for managing course projects, quizzes and homeworks.

\textbf{Compiler Design and Implementation} \hfill \textbf{Fall 2018}\\
{\it Instructors:  Dr. Fatemeh Ghassemi and Dr. Hosein Hojjat}\\
Responsible for designing main project of the course in 4 phases.\\ \\
\textbf{Artifical Intelligence} \hfill \textbf{Spring 2019}\\
{\it Instructor:  Dr. Mohammad Amin Sadeghi} \\
Responsible for designing a computer assignment for students to become familiar with naive Bayes and Bayesian network.

\textbf{Design and Analysis of Algorithms} \hfill \textbf{Fall 2017}\\
{\it Instructor:  Dr. Hamid Mahini}\\
Responsible for designing a homework about complexity of  algorithms.

\textbf{Theory of Formal Languages and Automata} \hfill \textbf{Fall 2017}\\
{\it Instructor:  Dr. Hakimeh Fadaei}\\ 
Responsible for designing two homeworks about regular expressions and pushdown automatons.

\textbf{Engineering Statistics and Probability} \hfill \textbf{Fall 2017}\\
{\it Instructor:  Dr. Behnam Bahrak}\\
Responsible for correction of a homework about conditional probability. \\ \\
\textbf{Data Structure and Algorithms} \hfill \textbf{Spring 2018}\\
{\it Instructor:  Dr. Fathieh Faghih}\\
Responsible for designing a computer assigment about basic data structures and implementing them.

\textbf{Data Structure and Algorithms} \hfill \textbf{Fall 2017}\\
{\it Instructor:  Dr. Hesham Faili}\\
Responsible for designing a computer assignment about graphs, DAGs and trees.



	% Language Skills
    \section{\mysidestyle Language\\Skills}
Persian: Native\\
English: Advanced - TOEFL: 104 (R:28 L:25 S:26 W:25)\\

	% Computer Skills
    \section{\mysidestyle Software Skills}

SpringBoot: 4/5\\Kotlin: 4/5\\ Java: 4/5 \\ Python:4/5\\ Django: 4/5 \\ Golang: 3/5 \\ KafkaStreams: 3/5\\NoSQLs(MongoDB, Cassandra, Redis): 3/5 \\ ElasticSearch: 3/5  \\ Kubernetes: 4/5 \\ MySql:3/5 \\Docker: 4/5 \\ Antlr: 3/5 \\  Apache Spark: 1/5\\
Angular: 2.5/5 \\
 C, C++: 3/5\\Javascript: 4/5\\
 React,React Native,React Redux : 3/5 \\Node.JS: 2/5\\ 
\textbf{Tools}:Git, \LaTeX \\
\textbf{Agile Methodology} : Scrum, XP \\
\textbf{Simulation}: Multisim,Modelsim, Quartus II, Pspice, Logic Gate Simulator

\end{resume}
\end{document}